### 2020-02-05 ncov.tex
minor tweak

Consistent with our previous observations (\fref{eff}),
we find that accounting for uncertainties in the estimate of $r$ has the largest effect on the estimates of \Ro\ in most cases (\fref{R0}).
For example, recalculating \Ro for Study 7 by using our pooled estimate of $r$ gives $\Ro = 3.9$ (95\% CI: 2.3--8.6), which is much wider than the uncertainty range they reported (2.0--3.1).
There are two explanations for this result.
First, even though the exponential growth rate $r$ and the mean generation interval $\bar G$ have identical mathematical effects on \Ro in our framework (\eref{gamma} in Methods),
$r$ is more influential in this case because it is associated with more uncertainty (\fref{assumption}).
Second, assuming a fixed generation interval ($\kappa=0$) makes the estimate of \Ro too sensitive to $r$ and $\bar G$.
One exception is Study 1: we find this estimate of \Ro is most sensitive to generation-interval dispersion $\kappa$.
This is because Study 1 assumes an exponentially distributed generation interval ($\kappa=1$): estimates that include this assumption make \Ro relatively insensitive and thus tend have particularly narrow confidence intervals.

>>>>

Consistent with our previous observations (\fref{eff}),
we find that accounting for uncertainties in the estimate of $r$ has the largest effect on the estimates of \Ro\ in most cases (\fref{R0}).
For example, recalculating \Ro for Study 7 by using our pooled estimate of $r$ gives $\Ro = 3.9$ (95\% CI: 2.3--8.6), which is much wider than the uncertainty range they reported (2.0--3.1).
There are two explanations for this result.
First, even though the exponential growth rate $r$ and the mean generation interval $\bar G$ have identical mathematical effects on \Ro in our framework (\eref{gamma} in Methods),
$r$ is more influential in this case because it is associated with more uncertainty (\fref{assumption}).
Second, assuming a fixed generation interval ($\kappa=0$) makes the estimate of \Ro too sensitive to $r$ and $\bar G$.
One exception is Study 1: we find this estimate of \Ro is most sensitive to generation-interval dispersion $\kappa$.
This is because Study 1 assumes an exponentially distributed generation interval ($\kappa=1$): estimates that rely on this assumption make \Ro relatively insensitive and thus tend to have particularly narrow confidence intervals.
